### 2016-06-23 NLO.tex
Latex does not compile any more
up to RSymmetry
NLO chapter

\subsection{The Cross Section in the Limit of Large Sgluon Masses}
The cross section for squark production does not exist in the limit of an infinitely large sgluon mass, instead it was found that it diverges logarithmically.\\
\begin{align}
\lim_{m_{\sigma^0}\to\infty} \sigma(qq \to \tilde{q}\tilde{q}) \sim \ln \frac{m_{\sigma^0}^2}{\mu^2}
\end{align}
This is actually expected as an effective field theory of the MRSSM where the sgluon is integrated out is no longer supersymmetric. This is because the sgluon is together with the octino part of a supermultiplet. Integrating out only the sgluon means that the octino misses its superpartner in the effective field theory. In this case the decoupling theorem \cite{Appelquist:1974tg} does no longer hold.\\
Refer to super oblique correction and quantify difference of $g$ and $\hat{g}$ from eq 4 in \cite{Cheng:1997sq}\\
append plot

>>>>

\subsection{The Squark Production Cross Section at Next-to-Leading Order}
The squark production cross section at next-to-leading order is composed out of three contributions. These are the Born or tree-level cross section, the virtual correction and the real correction. 
\sigma^{\mathrm{NLO}} = \sigma^{\mathrm{B}} + \sigma^{\mathrm{V}} + \sigma^{\mathrm{R}}\label{eq:BVR}
All three contributions have to be calculated with next-to-leading parton density functions.\\
It has been checked that for multiple different and quite distinct choices of the parameters $m_{\tilde{q}}$ and $m_{\tilde{g}}$ the double as well as the single poles of the virtual and real correction cancel up to machine precision. As the real corrections have been calculated analytically it is possible to quote the double pole. With
\sigma^{\mathrm{R}}_{\mathrm{double\ pole}} = -\sigma^{\mathrm{V}}_{\mathrm{double\ pole}} = C(F)\frac{\alpha_s}{\pi}\sigma^{\mathrm{B}} \frac{1}{\epsilon^2}
it has a very succinct form. \\
The setup of the calculation is summarized in fig. \ref{fig:CalcSetup}. Both the virtual and the Born matrix amplitude have been generated with the \texttt{Mathematica} package \texttt{FeynArts}. To this end a modelfile generated by the \texttt{Mathematica} package \texttt{SARAH} has been adjusted by hand to include counterterm Feynman rules and the definition of those counterterms. The matrix amplitudes have been processed further to the absolute squared matrix amplitudes by the \texttt{Mathematica} package \texttt{FormCalc} which have then been converted to \texttt{C++} and stored in an output file.\\
This output file is in turn invoked by a \texttt{C++} code which evaluates the scalar integrals of the absolute squared matrix amplitudes numerically by using the package \texttt{LoopTools} \cite{Hahn:1998}. Finally the phase space integration is performed by the integration routine "Cuhre" which is part of the \texttt{CUBA} library\cite{Hahn:2004fe}.\\
Comment on how real corrections are processed.\\
\begin{tikzpicture}
	\node [block4] at (-1,0) (Mathematica) {Mathematica notebook};
	\node [block1a] at (-1,-3) (notebookB) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{B}}$ \newline \texttt{FormCalc} $\to \sum |\mathcal{M}^{\mathrm{B}|^2}$};	
	\node [block1a] at (-1,-1.5) (notebookV) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{1L}}$ \newline \texttt{FormCalc} $\to \sum |\mathcal{M}^{\mathrm{V}|^2}$};
	\node [block5a] at (7.5,0) (C++) {\texttt{C++} code};
	\node [block5b] at (3.7,-3.5) (Born) {\underline{Born contribution} \newline \texttt{CUBA} $\to$ num. integration over $t, x_1, x_2$ to $\sigma^{\mathrm{B}}$};
	\node [block5b] at (7.5,-2.7) (Virt) {\underline{Virtual correction}\newline \texttt{LoopTools} $\to$ computation \newline of $ \sum |\mathcal{M}^{\mathrm{V}|^2}$ \newline \texttt{CUBA} $\to$ num. integration over $t, x_1, x_2$ to $\sigma^{\mathrm{V}}$};
	\node [block5c] at (11.5,-3.3) (Real) {\underline{Real correction}\newline \texttt{MADGRAPH} $\to$ $\mathcal{M}^{\mathrm{R}}$, phase space slicing\newline \texttt{CUBA} $\to$ num. integration to $\sigma^{\mathrm{R}}$};
	\path [line, line width = 1] (1.2,-3) -- (1.9,-3);
	\path [line, line width = 1] (1.2,-1.5) -- (5.7,-1.5);
	\node [block6a] at (7.5,-6.5) (Sigma) {$\sigma^{\mathrm{NLO}} = \sigma^{\mathrm{B}} + \sigma^{\mathrm{V}} + \sigma^{\mathrm{R}}$};
	\path [line, line width = 1] (Born) -- (Sigma);
	\path [line, line width = 1] (Virt) -- (Sigma);
	\path [line, line width = 1] (Real) -- (Sigma);
\caption{This scheme illustrates the setup of the computation of the next-to-leading order cross section. The absolute squared matrix amplitudes of the Born or tree-level contribution and the virtual correction are generated by \texttt{Mathematica} packages and imported into a \texttt{C++} code. Loop integrals are evaluated numerically using \texttt{Looptools}. For all three contributions the \texttt{CUBA}-library was used for the phase space and $x_1$ and $x_2$ integration to arrive at the cross sections $\sigma^{\mathrm{B}}$, $\sigma^{\mathrm{V}}$ and $\sigma^{\mathrm{V}}$.}\label{fig:CalcSetup}

\subsubsection{Remark on Prefactors in the Calculation}
For the discussion of results it will not been distinguished between virtual and real corrections. This is because they have not been separated strictly in the calculation: As already discussed both $\sigma^{\mathrm{V}}$ and $\sigma^{\mathrm{R}}$ are divergent, i.e. there are poles of the form $\frac{1}{\epsilon}$ and $\frac{1}{\epsilon^2}$. But these pole cancel completely. On the other hand there are also prefactors from the phase space integral and the loop integral, with can be expanded in a power series in $\epsilon$. In short, the virtual and real correction to the cross section can be expressed with some coefficients $A - E$, which are functions of the parameters $m_{\tilde{g}}$ and $m_{\tilde{q}}$, in the following way
\begin{align}
\sigma^{\mathrm{V}} &= \left( 1 + (A^{\mathrm{V}} + P_1)\epsilon + (B^{\mathrm{V}} + P_2)\epsilon^2 + \mathcal{O}(\epsilon^3) \right)\left( C^{\mathrm{V}} - \frac{D}{\epsilon} - \frac{E}{\epsilon^2} \right),\\
\sigma^{\mathrm{R}} &= \left( 1 + (A^{\mathrm{R}} + P_1)\epsilon + (B^{\mathrm{R}} + P_2)\epsilon^2 + \mathcal{O}(\epsilon^3) \right)\left( C^{\mathrm{R}} + \frac{D}{\epsilon} + \frac{E}{\epsilon^2} \right).\label{eq:prefactoredecomp}
\end{align}
Here, the coefficients $A$, $B$ and $C$ are in general distinct in the virtual and real part, but $D$ and $E$ are the same as the poles of both contributions cancel exactly.\\
Now some of the prefactors, namely $P_1$ and $P_2$, are the same in both contributions. Just keeping them like in eq. \eqref{eq:prefactoredecomp} would slow the computation of the real part down by a factor 5 because this part of the calculation is done analytically. Therefore a speed-up has been achieved by discarding the common prefactors at the cost of loosing track about the origin of the next-to-leading order correction.\\
A common prefactor comes from the two-body phase space integral in eq. \eqref{eq:diffsigma}
\begin{align}
\frac{(4\pi)^\epsilon}{\Gamma(1-\epsilon)}\left( \frac{tu - m_{\tilde{q}}^4}{\mu^2 s} \right)^{-\epsilon} = 1 &+ \epsilon\left( \ln 4\pi -\gamma_E - \ln \frac{tu - m_{\tilde{q}}^4}{\mu^2 s} \right) 
+ \epsilon^2\left( \frac{1}{2}\left( \ln 4\pi - \ln \frac{tu - m_{\tilde{q}}^4}{\mu^2 s} \right)^2 \right.\nonumber\\
&+ \left.\frac{\gamma_E^2}{2} - \frac{\pi^2}{12} - \gamma_E\left( \ln 4\pi - \ln \frac{tu - m_{\tilde{q}}^4}{\mu^2 s} \right) \right) + \mathcal{O}(\epsilon^3).\label{eq:PhasePrefactor}
\end{align}
In addition the prefactor of a loop integral defined in \texttt{LoopTools} differs from the one usually, and therefore also here, used. The \texttt{LoopTools} definition\cite{LoopToolsManual} of a loop integral is 
\begin{align}
T^N_{\mu_1\hdots\mu_P} = \frac{\mu^{4-D}}{i\pi^{\frac{D}{2}}r_\Gamma}\int\mathrm{d}^Dq\frac{q_{\mu_1} \hdots q_{\mu_P}}{[q^2-m_1^2] [(q+p_1)^2-m_2^2] \hdots [(q+p_1+ \hdots +p_{N-1})^2-m_N^2]}\label{eq:LoopToolsInt}
\end{align}
where $T^1$ is an $A$-integral, $T^2$ is an $B$-integral, etc. and $r_\Gamma = \frac{\Gamma(1-\epsilon)^2\Gamma(1+\epsilon)}{\Gamma(1-2\epsilon)}$, where $\Gamma(z)$ is the Gamma function. Comparing the prefactors of eq. \eqref{eq:LoopToolsInt} and eq.  \eqref{eq:LoopInt} one finds that one has to multiply the \texttt{LoopTools} output by
\begin{align}
r_\Gamma (4\pi)^\epsilon = 1 + \epsilon(\ln 4\pi -\gamma_E) + \epsilon^2\left( \frac{\gamma_E^2}{2} - \frac{\pi^2}{12} + \frac{\ln^2 4\pi}{2} - \gamma_E\ln 4\pi \right) + \mathcal{O}(\epsilon^3)\label{eq:LoopPrefactor}
\end{align}
in order to have the same prefactors as in eq. \eqref{eq:LoopInt}. The right hand side of eq. \eqref{eq:PhasePrefactor} and eq. \eqref{eq:LoopPrefactor} are the prefactors discarded in the computation. Instead the prefactor ??? has been included in the virtual correction.

\subsubsection{$K$-factors for Squark Production in the MRSSM}
A common way to describe next-to-leading order corrections is stating the $K$-factor, which is defined to be the ratio of the complete next-to-leading order cross section $\sigma^{\mathrm{NLO}}$, see eq. \eqref{eq:BVR} and the leading order cross section $\sigma^{\mathrm{LO}}$:
\begin{align}
K(X \to Y) = \frac{\sigma^{\mathrm{NLO}}(X \to Y)}{\sigma^{\mathrm{LO}}(X \to Y)}.
\end{align}
The process in question is described by $X \to Y$.
Figure \ref{fig:1LXsection_fixed_m} shows the $K$-factor for the production of up-squarks in the MRSSM for varying masses of both the squark ($m_{\tilde{g}} = \unit[2000]{GeV}$) and the gluino $m_{\tilde{q}} = \unit[1000]{GeV}$. The mass of the pseudoscalar has been fixed to $m_{\sigma} = \unit[5000]{GeV}$ in both plots. It can be seen that the  $K$-factor increases with increasing squark mass and decreases with increasing gluino mass. Note that the sum of virtual and real corrections gets negative for very light squarks. But this region of parameter space is already excluded phenomenologically.
\begin{figure}[!htpb]
\begin{center}
\includegraphics[scale=.5]{figures/MRSSM_uu_susu_Kfactors_msg=2000GeV.png}
\includegraphics[scale=.5]{figures/MRSSM_uu_susu_Kfactors_msq=1000GeV.png}
\caption{Dependence of the $K$-factor for the process $uu \to \tilde{u}\tilde{u}$ on the squark mass $m_{\tilde{q}}$ for fixed $m_{\tilde{g}} = \unit[2000]{GeV}$ (top) and on the gluino mass $m_{\tilde{g}}$ for fixed $m_{\tilde{q}} = \unit[1000]{GeV}$ (bottom).}\label{fig:1LXsection_fixed_m}
\end{center}
\end{figure}
Calculate uncertainties for multiple points(pdf, scale, integration)

\subsection{The Cross Section in the Limit of Large Sgluon Masses}
The cross section for squark production does not exist in the limit of an infinitely large sgluon mass, instead it was found that it diverges logarithmically.\\
\begin{align}
\lim_{m_{\sigma}\to\infty} \sigma(qq \to \tilde{q}\tilde{q}) \sim \ln \frac{m_{\sigma}^2}{\mu^2}
\end{align}
This is actually expected as an effective field theory of the MRSSM where the sgluon is integrated out is no longer supersymmetric. This is because the sgluon is together with the octino part of a supermultiplet. Integrating out only the sgluon means that the octino misses its superpartner in the effective field theory. In this case the decoupling theorem \cite{Appelquist:1974tg} does no longer hold.\\
It is even possible to predict the  logarithmic scaling of $\sigma(qq \to \tilde{q}\tilde{q})$ quantitatively. The coefficient of the logarithm is proportional to the difference of the one-loop $\beta$ function coefficients of $g_s$ and $\hat{g}_s$ in the effective theory with the heavy particle integrated out, see eq. (4) in \cite{Cheng:1997sq}.
\begin{figure}[!htpb]
\begin{center}
\includegraphics[scale=.5]{figures/MRSSM_uu_susu_Kfactors_msq=1000GeV_msg=2000GeV.png}
\caption{Dependence of the $K$-factor for the process $uu \to \tilde{u}\tilde{u}$ on the mass of the pseudoscalar sgluon. For $m_{\sigma} \approx \unit[10^5]{GeV}$ onwards want find a logarithmic scaling as predicted by \cite{Cheng:1997sq}.}
\end{center}
\end{figure}
